Homicide Increases in the COVID-19 Era

### 2025-02-21 Draft1.qmd
Added references and began Plot 6
Added maps

@@

```

@@

zcta_filtered <- zcta %>% inner_join(LA_zctas, by = "ZCTA5CE20")

median_household_income <- cali_median_income %>% select(ZCTA, S1903_C03_001E, year)

@@

zcta_no_NAs <- zcta_with_data %>% filter(!is.na(S1903_C03_001E))

plot(st_geometry(zcta_with_data), 
     col = brewer.pal(9, "Blues")[as.numeric(cut(zcta_with_data$S1903_C03_001E, 
                                                 breaks = 9))], 
     border = 'grey', 
     axes = TRUE, 
     main = "Median Household Income by Year and Zip Code", 
     cex.main = 1.5)
```

@@

# Interpretation

>>>>

The codebook for this dataset can be found here: https://data.lacity.org/Public-Safety/Crime-Data-from-2020-to-Present/2nrs-mtv8/about_data.

@@

```
# Interpretation

@@

# joining the zcta shape file with LA zcta reference file
zcta_filtered <- zcta %>% inner_join(LA_zctas, by = "ZCTA5CE20")

# getting LA median income using joined file
median_household_income <- cali_median_income %>% select(ZCTA, S1903_C03_001E, year)

@@

# remove NAs
zcta_no_NAs <- zcta_with_data %>% filter(!is.na(S1903_C03_001E), S1903_C03_001E != "-")

palette <- brewer.pal(7, "Greens")

par(mfrow = c(2, 3), mar = c(2, 2, 2, 6), oma = c(0, 0, 4, 0))

yrs <- 2018:2023

for (yr in yrs) {
  # Filter by year
  subset_data <- zcta_no_NAs[zcta_no_NAs$year == yr, ]

  # Divide it into bins
  bins <- cut(subset_data$S1903_C03_001E, breaks = 7, labels = FALSE)

  # Plot
  plot(st_geometry(subset_data),
       col = palette[bins],
       border = 'grey',
       axes = FALSE,
       main = yr,
       cex.main = 1.5)

  # Add legend
  legend("right", inset = c(-0.5, 0), legend = round(quantile(subset_data$S1903_C03_001E, probs = seq(0, 1, length.out = 7)), 0),
         fill = palette, title = "Median Income ($)", bty = "n", cex = 0.8, xpd = TRUE)
}
mtext("Median Household Income by Year and Zip Code in LA", outer = TRUE, cex = 1, font = 2)
```

@@

```{r}
crime_frequency <- data.frame(table(crime_la$Crm.Cd.Desc))
top_10_crimes <- crime_frequency[order(-crime_frequency$Freq), ][1:10, ]
```
